Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-09 robdml.tex
tex

\noindent\textbf{III. Intra-Class Structure.}
%
$L_\text{ICS}$ is independent to HM, but is not incompatible with ACT as it
does not create adversarial anchor.
%
Thus, we validate this loss term with HM.
%
As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining robustness (especially
intra-class-wise), while retaining an acceptable trade-off in R@1.

@@

Further technical details, discussions, limitations and societal impact of our
method are presented in supplementary.

>>>>

\noindent\textbf{III. Intra-Class Structure.}
%
$L_\text{ICS}$ is independent to HM, but is incompatible with ACT as it
does not create adversarial anchor.
%
Thus, we validate this loss term with HM.
%
As shown in \cref{tab:ics} and \cref{fig:ics}, $L_\text{ICS}$ consistently
leads to a higher efficiency in gaining robustness (especially
intra-class-wise), while retaining an acceptable trade-off in R@1.

@@

Further experiment discussions, technical details, limitations and societal
impact are presented in supplementary.
